% https://www.rpi.edu/dept/arc/training/latex/resumes/
% LaTeX resume using res.cls
\documentclass[]{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font 
\setlength{\textwidth}{5.1in} % set width of text portion
%\usepackage[margin=1in]{geometry}
%\usepackage[top=2cm,bottom=2cm,left=2cm,right=4cm]{geometry}


\usepackage{etaremune}
\renewcommand{\labelenumi}{[\theenumi]}
\usepackage{enumitem }

\begin{document}

% Center the name over the entire width of resume:
 \moveleft.5\hoffset\centerline{\large\bf Rimpei Chiba}
% Draw a horizontal line the whole width of resume:
 \moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip
% address begins here
% Again, the address lines must be centered over entire width of resume:
 %\moveleft.5\hoffset\centerline{Postdoctoral Fellow, Canadian Institute for Theoretical Astrophysics (CITA)}
 %\moveleft.5\hoffset\centerline{University of Toronto, 60 St. George Street, Toronto, ON, M5S 3H8, Canada}
 %\moveleft.5\hoffset\centerline{rchiba@cita.utoronto.ca}
 \moveleft.5\hoffset\centerline{JSPS Postdoctoral Fellow, The University of Tokyo}
 \moveleft.5\hoffset\centerline{7-3-1, Hongo, Bunkyo-ku, Tokyo, 113-0033, Japan}
 \moveleft.5\hoffset\centerline{rimpei-chiba@g.ecc.u-tokyo.ac.jp}
 \moveleft.5\hoffset\centerline{ORCID: 0000-0002-3445-855X}


\begin{resume}

\section{EMPLOYMENT}
\noindent
\begin{tabbing}
    2025 - 2028 \hspace{2mm} \=\textbf{JSPS Postdoctoral Fellow}, University of Tokyo\\
    2022 - 2025 \hspace{2mm} \=\textbf{CITA Postdoctoral Fellow}, University of Toronto
\end{tabbing}

\section{EDUCATION}
\noindent
\begin{tabbing}
    2018 - 2022 \hspace{2mm} \={\sl D.Phil. in Theoretical Physics,} University of Oxford\\
    2016 - 2018 \hspace{2mm} \>{\sl M.Sc. in Physics,} Tokyo Institute of Technology \& TU Wien\\ 
    2012 - 2016 \hspace{2mm} \>{\sl B.Sc. in Aerospace Engineering,} Tokyo Institute of Technology
\end{tabbing}

\section{PUBLICATION}
\noindent
\subsection{Leading authors}
\begin{etaremune}[leftmargin=6mm,rightmargin=-6mm]
    \item \textbf{Chiba R.}, Ding J., Hamilton C., Kunz M. W., Tremaine S., Galactic echoes, \\
    arXiv:2505.16512, (2025)
    \item \textbf{Chiba R.}, Frankel N., Hamilton C., Origin of the two-armed vertical phase-spiral in the inner Galactic disk, arXiv:2503.20869, (2025)
    \item \textbf{Chiba R.}, Kataria S. K., Origin of reduced dynamical friction by dark matter halos with net prograde rotation, Mon. Not. R. Astron. Soc., 528, 4115-4124 (2024)
    \item \textbf{Chiba R.}, Dynamical friction and feedback on galactic bars in the general fast-slow regime, Mon. Not. R. Astron. Soc., 525, 3576-3596 (2023)
    \item \textbf{Chiba R.}, Schönrich R., Oscillating dynamical friction on galactic bars by trapped dark matter, Mon. Not. R. Astron. Soc., 513, 768-787 (2022)
    \item \textbf{Chiba R.}, Schönrich R., Tree-ring structure of Galactic bar resonance, Mon. Not. R. Astron. Soc., 505, 2412-2426 (2021)
    \item \textbf{Chiba R.}, Jennifer F., Schönrich R., Resonance sweeping by a decelerating Galactic bar, Mon. Not. R. Astron. Soc., 500, 4710-4729 (2021)
    \item \textbf{Chiba R.}, Ishikawa Y., Hasegawa J., Horioka K., Time evolution of laser-ablation plumes and induced shock waves in low-pressure gas, American Institute of Physics, Physics of Plasmas, 24, 063520 (2017)
\end{etaremune}
\noindent
\subsection{Co-authors}
\begin{etaremune}[leftmargin=6mm,rightmargin=-6mm]
    \item Géron T., Smethurst R. J., Dickinson H., Fortson L. F., Garland I. L., Kruk S., Lintott C., Makechemu J. S., Mantha K. B., Masters K. L., O'Ryan D., Roberts H., Simmons B. D., Walmsley M., Calabrò A., \textbf{Chiba R.}, Costantin L., Drout M. R., Fragkoudi F., Guo Y., Holwerda B. W., Jogee S., Koekemoer A. M., Lucas R. A., Pacucci F., Galaxy Zoo CEERS: Bar fractions up to $z\sim 4.0$, arXiv:2505.01421, (2025)
    \item Li C., Yuan Z., Monari G., Martin N. F., Siebert A., Famaey B., \textbf{Chiba R.}, Kordopatis G., Ibata R. A., Hill V., Exploring the impact of a decelerating bar on transforming bulge orbits into disc-like orbits, A\&A, Vol 690, A26 (2024)
    \item Yuan Z., Li C., Martin N. F., Monari G., Famaey B., Siebert A., \textbf{Chiba R.}, Ardern-Arentsen A., Sestito F., Thomas G. F.,7, Hill V., Ibata R. A., Kordopatisc G., Starkenburg E., Viswanathan A., A\&A, Vol 691, L1 (2024)
    \item Szabo P., \textbf{Chiba R.}, Biber H., Stadlmayr R., Berger B., Mayer D., Mutzke A., Doppler M., Sauer M., Appenroth J., Fleig J., Foelske-Schmitz A., Hutter H., Mezger K., Lammer H., Galli A., Wurz P., Aumayr F., Solar wind sputtering of wollastonite as a lunar analogue material -- Comparisons between experiments and simulations, Icarus, Vol 314, 98-105 (2018)
\end{etaremune}

\section{SCHOLARSHIPS AND AWARDS}
\noindent
\begin{tabbing}
    2025 - 2028 \hspace{2mm} \=\textbf{JSPS Postdoctoral Fellowship}\\
    2022 - 2025 \hspace{2mm} \=\textbf{CITA Postdoctoral Fellowship}\\
    2018 - 2022 \hspace{2mm} \=\textbf{Takenaka Scholarship} for overseas studies\\
    2018        \hspace{2mm} \>\textbf{Best Master Thesis Award} (Tokyo Institute of Technology)\\
    2017        \hspace{2mm} \>\textbf{Young Poster Award} (International Astronomical Union, Symposium 335)\\
    2016 - 2017 \hspace{2mm} \>\textbf{Tobitate Scholarship} (Japan Young Ambassador Program)
\end{tabbing}

\section{SCIENTIFIC PRESENTATION}
\noindent
\begin{tabbing}
    02/2025 \hspace{2mm} \=Talk, Como Lake centre for AstroPhysics, Colloquium (Como, Italy)\\
    01/2025 \hspace{2mm} \=Talk, Conference IAStrophysical Waves (Princeton, US)\\
    09/2024 \hspace{2mm} \>Talk, Nanjing University, Astrophysics seminar (Nanjing, China)\\
    09/2024 \hspace{2mm} \>Talk, Conference ``Waves in the Milky Way Disk'' (Shanghai, China)\\
    06/2024 \hspace{2mm} \>Blackboard Talk, KITP Program ``Interconnections between the Physics of Plasmas\\
                         \>and Self-gravitating Systems'' (Santa Barbara, US)\\
    01/2024 \hspace{2mm} \>Talk, Shanghai Jiao Tong University, Astronomy seminar (Shanghai, China)\\
    09/2023 \hspace{2mm} \>Talk, Institute for Advanced Study, Astrophysics seminar (Princeton, US)\\
    07/2023 \hspace{2mm} \>Poster, Galactic bars: driving and decoding galaxy evolution (Granada, Spain)\\
    06/2023 \hspace{2mm} \>Talk, Canadian Astronomical Society, Annual meeting (Penticton, Canada)\\
    12/2022 \hspace{2mm} \>Talk, CITA seminar (Toronto, Canada)\\
    11/2022 \hspace{2mm} \>Talk, University of Leicester, Astrophysics seminar (Leicester, UK)\\
    01/2022 \hspace{2mm} \>Talk, University College London, MSSL seminar (London, UK)\\
    07/2021 \hspace{2mm} \>Talk, National Astronomy Meeting (Bath, UK)\\
    02/2021 \hspace{2mm} \>Talk, University of Oxford, Galaxy Journal Club seminar (Oxford, UK)\\
    07/2020 \hspace{2mm} \>Talk, European Astronomical Society, Annual meeting (Leiden, Sweden)\\
    12/2019 \hspace{2mm} \>Talk, University of Surrey, Milky Way Local Group seminar, (Surrey, UK)\\
    09/2017 \hspace{2mm} \>Talk, The Physical Society of Japan, Annual meeting (Iwate, Japan)\\
    07/2017 \hspace{2mm} \>Poster, International Astronomical Union, Symposium 335 (Exeter, UK)\\
    04/2017 \hspace{2mm} \>Poster, European Geoscience Union, General Assembly (Vienna, Austria)\\
    01/2016 \hspace{2mm} \>Talk, National Institute of Fusion Science, Conference (Gifu, Japan)
\end{tabbing}

\section{ACADEMIC SERVICES}
\noindent
\begin{tabbing}
    2022 - 2025 \hspace{2mm} \=CITA blackboard seminar, organizer\\
    Review: \>Monthly Notices of the Royal Astronomical Society, Astronomy \& Astrophysics, \\
    \>Astrophysical Journal
\end{tabbing}

\section{SKILLS}
\noindent
\begin{tabbing}
    Computing: \=C/C++, python, MPI, OpenMP \\
    Language: \>Japanese (native), English (fluent)
\end{tabbing}


\section{REFERENCES}
\begin{itemize}[leftmargin=*]
    \item \textbf{Ralph Sch\"onrich}\\
    Mullard Space Science Laboratory, University College London\\
    r.schoenrich@ucl.ac.uk
    \item \textbf{John Magorrian}\\
    Rudolf Peierls Centre for Theoretical Physics, University of Oxford\\
    john.magorrian@physics.ox.ac.uk
    \item \textbf{James Binney}\\
    Rudolf Peierls Centre for Theoretical Physics, University of Oxford\\
    james.binney@physics.ox.ac.uk
    %\item \textbf{Juna Kollmeier}\\
    %Canadian Institute for Theoretical Astrophysics, University of Toronto\\
    %jak@cita.utoronto.ca
    \item \textbf{Peter Martin}\\
    Canadian Institute for Theoretical Astrophysics, University of Toronto\\
    pgmartin@cita.utoronto.ca
    \item \textbf{Scott Tremaine}\\
    School of Natural Sciences, Institute for Advanced Study\\
    tremaine@ias.edu
    \item \textbf{Michiko Fujii}\\
    Department of Astronomy, University of Tokyo\\
    fujii@astron.s.u-tokyo.ac.jp
    %\item \textbf{Jun Hasegawa}\\
    %Institute of Innovative Research, Tokyo Institute of Technology\\
    %jhasegawa@zc.iir.titech.ac.jp
\end{itemize}


\end{resume}
\end{document}




